Make the full map of Tanzania land cover

### 2022-03-06 docs/run_experiments.Rmd
Ready to run

- Random scale
- Random flip (always use)
- Random center rotate
- Normalization
    - Dataset based standardization
    - Image based standardization
    - Image based min-max scaler

>>>>

- Random flip (always use)
- Random scale
- Random center rotate
- Normalization: Dataset based standardization. *Among dataset-based standardization, image-based standardization, image-based normalization, and no such transformation, dataset-based standardization works the best because the U-Net learned much faster.*

#### Hierachical training

- Train a big model using the whole dataset over the whole area.
- Fine tune (or transfer) the model into 5 sub zones.

Records:

### 2022-03-06 docs/tanzania_full_map.Rmd
Ready to run

- Using all bands and image standardization
- Using all bands without image standardization
- Using only NICFI bands with image standardization
- Using only NICFI bands without image standardization

>>>>

- Using all bands with image augmentation including image standardization
- Using only NICFI bands with image augmentation including image standardization （* This provides option of prediction for other years, it is much faster to prepare satellite images).
